Analyses

### 2021-12-08 src/analysis/analyses.Rmd
add analyses

## Ethnic Conception Hypothesis 
```{r "h1", fig.align="center", fig.height=5, fig.width=6}
source(here("src/analysis/h1.R"))
p1
# negative values: Ethnic conception > Civic conception 
# positive values: Ethnic conception < Civic conception 
```

## National Identity Hypothesis
```{r "h2a", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2a.R"))
p2a
```

## Far Right Party ID Hypothesis
```{r "h2b", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2b.R"))
p2b
```

@@

## Alternative specifications + Interactions

@@

pe3/ (pe4 + pe5) #add pe2 (age)
```

@@

## Explanatory Power: Predicting Populist Vote
```{r "predict-vote-1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-scales.R"))
exp1
```

```{r "predict-vote-2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-items.R"))
exp1
```

## Save Data with Scales
```{r "save data"}
save(d, file = here("data/intermediate/cleaned_experiment_scales.RData"))
```

>>>>

## Ethnic Conception Hypothesis 
```{r "h1", fig.align="center", fig.height=5, fig.width=6}
source(here("src/analysis/h1.R"))
p1
# negative values: Ethnic conception > Civic conception 
# positive values: Ethnic conception < Civic conception

kbl(df, booktabs =T, caption = "Ethnic Conception Hypothesis - T-Test") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "8cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2cm")
```

## National Identity Hypothesis
```{r "h2a", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2a.R"))
p2a

h2a <- h2a %>% 
  mutate(y = recode(y,
                    `POST_2` = "DV: People, not politicians, should make the most \n important political decisions",
                    `POST_3` = "DV: MPs should follow the will of the \n people",
                    `POST_4` = "DV: Differences between elites an the people are bigger than \n differences between the people")) %>%
  select(y, AME:lower, a) %>%
  rename(`Exclusive National Identity` = a)

kbl(h2a, booktabs =T, caption = "National Identity Hypothesis - AME") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "8cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm") 
```

## Far Right Party ID Hypothesis
```{r "h2b", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2b.R"))
p2b

h2b <- h2b %>% 
  mutate(y = recode(y,
                    `POST_2` = "DV: People, not politicians, should make the most \n important political decisions",
                    `POST_3` = "DV: MPs should follow the will of the \n people",
                    `POST_4` = "DV: Differences between elites an the people are bigger than \n differences between the people"),
         ethnic = recode(ethnic,
                         `1` = "Ethnic Conception of the People",
                         `0` = "Civic Conception")) %>%
  select(y, AME:lower, treatment = ethnic)

kbl(h2b, booktabs =T, caption = "Far Right Party ID - AME") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "8cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm") 
```

@@

@@

exp1 <- exp1 %>%
  mutate(y = recode(y,
                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
                    `POST_3` = "DV: MPs should follow \n the will of the people"))
kbl(exp1, booktabs =T, caption = "Ethnic Conception Hypothesis - OLS Effect of Ethnic Conception of the People ") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "8cm")

#(pe2 + pe3)/ (pe4 + pe5)
```

@@

## Explanatory Power: Predicting Populist Vote
```{r "predict-vote-1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-scales.R"))
exp1

exp <- exp %>%
  dplyr::select(estimate, lower, upper, scale = id, treatment = ethnic, y)
kbl(exp, booktabs =T, caption = "Explanatory Power: Scales Predicting Populist Vote - OLS Regression") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "4cm") %>%
  column_spec(5, width = "4cm") %>%
  column_spec(6, width = "4cm")
```

```{r "predict-vote-2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-items.R"))
exp1

exp <- exp %>%
  dplyr::select(estimate, lower, upper, item = id, treatment = ethnic, y)
kbl(exp, booktabs =T, caption = "Explanatory Power: Items Predicting Populist Vote - OLS Regression") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "4cm") %>%
  column_spec(5, width = "4cm") %>%
  column_spec(6, width = "4cm")
```
